HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
typo

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}, or the
annotators are explicitly asked to mark errors, which however suffer from even
lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes metrics
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is HMEANT
\parcite{lo2011structured}.
%More recent work on MT evaluation proposed measures
%that decompose

>>>>

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}, or the
annotators are explicitly asked to mark errors, which however suffers from even
lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes metrics
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is HMEANT
\parcite{lo2011structured}.
%More recent work on MT evaluation proposed measures
%that decompose
